Modalities for Location Virtualization

### 2022-09-20 programlogic.tex
a couple notes
+
quick comment

@@

>>>>

\todo[inline]{These fractions aren't quite right (though I see you added the variance between levels), I can walk you through in our meeting tomorrow.}

@@

\todo[inline]{We don't need to talk about sexec at all. Let's also talk tomorrow about adjusting the syntax in the paper to mimic actual textual assembly more closely (e.g., all of the instructions are mov, with different argument shapes)}

\mytodo{STOP HERE}
